---
title: "Lab5vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Lab5vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


#Installation
To install the Lab5 package , you need to source it from Github: devtools::install_github("NAZLIBILGIC/Lab5").

```{r setup}
library("Lab5")
library("jsonlite")
library("httr")
```


#Installation and usage
To use the package Lab5 , first, make sure you have the required libraries installed.



#installation required
Install and load the required packages-libraries.
#```{r}
#install.packages("shiny")
#library(shiny)
#```


#installation required
#```{r}
#install.packages("httr")
#library(httr)
#```

#installation required
#```{r}
#install.packages("jsonlite")
#library(jsonlite)
#```

```{r}
library("Lab5")
```

# 
List of City Bike API URLs for two cities
```{r}
city_api_urls <- c(
  "http://api.citybik.es/v2/networks/lundahoj",
  "http://api.citybik.es/v2/networks/malmobybike"
)
```


#
Calling the function provides information about the city bikes
```{r}
city_results <- Lab5::fetchCityBikeData(city_api_urls)
```


```{r}
lund_res <- fetchCityBikeData(api_urls = "http://api.citybik.es/v2/networks/lundahoj")
# Print empty slots of busiest station in Lund
lund_res$lundahoj$busiest$empty_slots
```



#Reading JSON data from local files
#```{r}
#lundahoj_data <- jsonlite::fromJSON("lundahoj_data.json")
#malmobybike_data <- jsonlite::fromJSON("malmobybike_data.json")
#data<-c(lundahoj_data,malmobybike_data)
#```



#
#To retrieve city bike station status information for Malmo:
#```{r}
#fetchCityBikeData(city_data = "malmobybike_data.json")
#results <- fetchCityBikeData(city_data)
#```


#
#To retrieve city bike station status information for Lund:
#```{r}
#findBusiestStationsFromData(city_data = "lundahoj_data.json", lundahoj)
#```




#Shiny App
There is a shiny app provided in the package in which the user selects a city and then gets automatically information about the most and least busy city bike stations there. The station name , the address of the location and the amount of free bikes available are given.
It can be opened: shiny::runGitHub('NAZLIBILGIC/lab5', subdir = "ShinyAppBike")

