---
title: "Lab5vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Lab5vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


#Installation
To install the Lab5 package , you need to source it from Github: devtools::install_github("NAZLIBILGIC/Lab5").

```{r setup}
library("Lab5")
library(jsonlite)
```


#Installation and usage
To use the package Lab5 , first, make sure you have the required libraries installed.



#installation required
Install and load the required packages-libraries.
#```{r}
#install.packages("shiny")
#library(shiny)
#```


#installation required
#```{r}
#install.packages("httr")
#library(httr)
#```

#installation required
#```{r}
#install.packages("jsonlite")
#library(jsonlite)
#```




# 
List of City Bike API URLs for two cities
```{r}
city_api_urls <- c(
  "http://api.citybik.es/v2/networks/lundahoj",
  "http://api.citybik.es/v2/networks/malmobybike"
)
city_results <- list()
```



Reading JSON data from local files
```{r}
lundahoj_data <- jsonlite::fromJSON("lundahoj_data.json")
malmobybike_data <- jsonlite::fromJSON("malmobybike_data.json")
data<-c(lundahoj_data,malmobybike_data)
```



#
To retrieve city bike station status information for Malmo:
```{r}
findBusiestStationsFromData(city_data = "malmobybike_data.json", malmobybike)
```


#
To retrieve city bike station status information for Lund:
```{r}
findBusiestStationsFromData(city_data = "lundahoj_data.json", lundahoj)
```


```{r}
for (city_id in names(city_results)) {
  results <- city_results[[city_id]]

  cat(paste("City:", city_id, "\n"))

  # Print Busiest Station Details
  cat("Busiest Station Details:\n")
  cat("Name: ", results$busiest$name, "\n")
  cat("Address: ", results$busiest$extra$address, "\n")
  cat("Free Bikes: ", results$busiest$free_bikes, "\n")

  # Print Least Busy Station Details
  cat("Least Busy Station Details:\n")
  cat("Name: ", results$least_busy$name, "\n")
  cat("Address: ", results$least_busy$extra$address, "\n")
  cat("Free Bikes: ", results$least_busy$free_bikes, "\n")
}
```





