---
title: "Lab5vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Lab5vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(Lab5)
```

#Introduction

This vignette provides documentation regarding how to use the `bikeStationStatus` function and "bikeStationStatu" function to retrieve bike station status information for multiple network IDs and provides information about the busiest and the least busy city bike station in a selected city. Furthermore, there is a shiny app created which is interactive with the user. The user picks a city and then automatically the results appear on the screen.



#Installation and usage

To use the package Lab5 , first, make sure you have the required libraries installed.

```{r}
# Install and load the required packages-libraries.
install.packages("shiny")
library(shiny)
install.packages("httr")
library(httr)
install.packages("jsonlite")
library(jsonlite)

```



#To decide the busiest and least busy station
```{r}
sample_city_info <- list(
    network = list(
      stations = data.frame(
        name = c("Station A", "Station B"),
        free_bikes = c(10, 5),
        extra = list(address = c("Address A", "Address B")),
        empty_slots=c(5,10))))
```



#To retrieve city bike station status information
```{r}
bikeStationStatu(sample_city_info)
```










